Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-06 paper/ms.tex
reviewed captions

\begin{figure*}
\begin{center}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Left panel. Distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field. Right panel. Surface density of dark 
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents one of the
  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
  in the Bolshoi simulation. The horizontal gray band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern.}
\end{center} 
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
    occ}$ (right) planes for all models with  KS test values
  $P>0.05$. The color code corresponds to the number of mock surveys
  compatible with observations. Only regions of parameter  space with
  at least one consistent mock survey are
  included. \label{fig:landscape}}      
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green line to observations by \citet{Ouchi2010}. The error
bars in the theoretical data correspond to the quadratic average of
the fitting errors for each mock
survey \label{fig:correlation_parameters}} 
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function. The observational data corresponds to
  \citet{Ouchi2010}.   
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.5 &10.6 & 0.3 & 0.1 \\
 10.6 &10.7 & 0.4 & 0.1 \\
 10.7 &10.8 & 0.5 & 0.1 \\
 10.8 &10.9 & 0.6 & 0.1 \\
 10.8 &11.0 & 0.4 & 0.2 \\
 10.9 &11.0 & 0.8 & 0.1 \\
 10.9 &11.0 & 0.9 & 0.1 \\
 10.9 &11.1 & 0.5 & 0.2 \\
 10.9 &11.3 & 0.3 & 0.4 \\
 11.0 &11.1 & 1.0 & 0.1 \\
 11.0 &11.2 & 0.6 & 0.2 \\
 11.0 &11.4 & 0.4 & 0.4 \\
 11.1 &11.3 & 0.7 & 0.2 \\
 11.1 &11.3 & 0.8 & 0.2 \\
 11.1 &11.4 & 0.6 & 0.3 \\
 11.2 &11.4 & 0.9 & 0.2 \\
 11.2 &11.4 & 1.0 & 0.2 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 0.4 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
\end{table}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Left panel. Distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field. Right panel. Surface density of dark 
  matter halos as a function of a minimum halo mass. Each line
  represents one of the $210$ volumes of dimensions $46\times 35\times
  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
  gray band represents the range of surface densities observed for
  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
  line the observational results by \citet{Ouchi2008}.}
\end{center} 
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs in a mock
  survey with model parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern.}
\end{center} 
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
    occ}$ (right) planes for all models with  KS test values
  $P>0.05$. The color code corresponds to the number of mock surveys
  compatible with observations. Only regions in the parameter space with
  at least one consistent mock survey are
  included. \label{fig:landscape}}      
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green line to observations by \citet{Ouchi2008,Ouchi2010}. The error
bars in the theoretical data correspond to the quadratic average of
the fitting uncertainties for each mock
survey \label{fig:correlation_parameters}}  
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function. The observational data for the ACF
  corresponds to 
  \citet{Ouchi2008,Ouchi2010}.   
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.5 &10.6 & 0.3 & 0.1 \\
 10.6 &10.7 & 0.4 & 0.1 \\
 10.7 &10.8 & 0.5 & 0.1 \\
 10.8 &10.9 & 0.6 & 0.1 \\
 10.8 &11.0 & 0.4 & 0.2 \\
 10.9 &11.0 & 0.8 & 0.1 \\
 10.9 &11.0 & 0.9 & 0.1 \\
 10.9 &11.1 & 0.5 & 0.2 \\
 10.9 &11.3 & 0.3 & 0.4 \\
 11.0 &11.1 & 1.0 & 0.1 \\
 11.0 &11.2 & 0.6 & 0.2 \\
 11.0 &11.4 & 0.4 & 0.4 \\
 11.1 &11.3 & 0.7 & 0.2 \\
 11.1 &11.3 & 0.8 & 0.2 \\
 11.1 &11.4 & 0.6 & 0.3 \\
 11.2 &11.4 & 0.9 & 0.2 \\
 11.2 &11.4 & 1.0 & 0.2 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
\end{table}
